---
output: 
  html_document: 
    keep_md: yes
---

A package level alternative for `options` and `getOptions`, to prevent cluterring the space. 

- ability to store all default options as a tab delimited table
- automatically check if file.path exists for options relating to files.
- fetch multiple options as list
- print options as a pretty table


### Installation

```{r eval=FALSE}
install.packages("params")
devtools::install_github("sahilseth/params")
```


#### Simple options

```{r message=FALSE, comment=""}
library(params)
set_opts(list(verbose = TRUE, 
	my_dir = "~/mypath",
	regex = "(.*)-[ATGC]{1}"))
get_opts("my_dir") ## extract options
```


#### example conf file

```{r}
conf = system.file("conf/params.conf", package = "params")
```

#### load the config file
```{r comment=""}
load_conf(conf)
```

#### load the config file in silence
```{r comment=""}
opts = load_conf(conf, check = FALSE, verbose = FALSE)
print(opts) ## print opts as a pretty table
```

#### Show all options
- notice how `my_conf_path` autocompleted {{{my_path}}}, getting its value from previous lines

```{r comment=""}
get_opts() 
```


**Here is what the original file looks like**:
```{r,comment="", echo=FALSE}
cat(paste(readLines(conf), collapse = "\n"))
```


#### Using params in your own package

params creates a environment object and stores all parameters in that object. If there are multiple packages loaded, which are using params, they 
may override each other's options, clutering the space the same way as options(). Alternatively, one may create a `env` for a package.


If you would like to use params in your R packages, use the following lines

```{r}
## Create a R file in your package, and put the following lines in it

#' @export
mypkg_opts = new.env()

#' @importFrom params get_opts
get_opts <- function(x){
	params::get_opts(x, envir = mypkg_opts)
}

#' @importFrom params set_opts
set_opts <- function(x){
	params::set_opts(x, envir = mypkg_opts)
}
```


Also, you would need to add `params` to the depends field in the `DESCRIPTION` file.


